### 2016-09-05 results.tex
adding scheme descriptions and updating text

\jnote{Organize by scheme, not by security notions.
}

\heading{Linear-PRF construction. }
Here we consider a set-multiplicity data structure that was attacked by Neidermayer et al. in~\cite{xxx}.  Let $\Pi_{\mathrm{lin}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be defined as follows. Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$. The queries are defined so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.  Fix non-empty sets ~$\calK$, $\univ$ and integers $k,m,n>0$.  Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family. Define $\Hash$ as an algorithm that samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [1,k]$.  $\Rep$ uses $\Hash$ to set $\privaux=\pubaux = (h_1, \ldots, h_k)$, computes an $m$ bit array, $M$ in the standard way and returns $(M,\pubaux,\privaux)$.  The $\Qry$ algorithm gets $(M,\privaux, q_x)$ as input, and returns the AND of values at $M[h_1(x)],\ldots,M[h_k(x)]$. It must be noted that $\Pi_{\mathrm{lin}}$ admits errors in form of false-positives(FP) only. So, error rate of $\Pi_{\mathrm{lin}}$ is same as the (non-adaptive) FP rate. The following result shows, informally, that if~$F$ is a good PRF and the error rate is sufficiently small, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries. Henceforth, we refer errors and error-rate in $\Pi_{\mathrm{lin}}$ as FP's and FP rate, respectively.

>>>>

\jnote{Organize by scheme, not by security notions.
}
\include{scheme-descriptions}

\heading{Linear-PRF construction. }
Here we consider a set-multiplicity data structure that was attacked by Neidermayer et al. in~\cite{xxx}. Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).  The following result shows, informally, that if~$F$ is a good PRF, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.

### 2016-09-05 syntax.tex
adding scheme descriptions and updating text

\heading{Data structures.}  We being by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset.
%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$, and a set of multisets~$\calS$ over
$\univ$. 
A \emph{data structure} (for $\calS$) is a tuple $\setprim=(\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
\item $\Rep \colon \mathcal{S} \to \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
    \emph{private representation data} $\privaux \in \bits^*$, and
    \emph{public representation data} $\pubaux \in \bits^*$.  We write
    $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
\item $\Qry\colon \Sigma^* \times \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $\pubaux,\privaux \in
    \bits^*$ and $q \in \calQ$, and outputting
    an \emph{answer} $a \in \Gamma$.  We write $a \gets
    \Qry(\pubaux,\privaux,q)$ for this execution.
\end{itemize}
\hfill\dqed
\end{definition}

@@

\begin{definition}[Error probability and rate] \rm
Fix a data structure $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep,
\Qry)$. Let $\mathrm{Err}(S,q,M,\pubaux,\privaux)$ be a predicate that is
true iff $\Qry(M, \pubaux,\privaux, q) \neq q(S)$.  Then a data structure
has \emph{error probability} $\epsilon$ if
$\max_{S,q}\Pr[(M,\pubaux,\privaux) \getsr \Rep(S) :
\mathrm{Err}(S,q,M,\pubaux,\privaux)=1 ] \leq \epsilon$.
%
It has \emph{error rate} $\tilde{\epsilon}$ if
$\max_{S}\Pr[(M,\pubaux,\privaux) \getsr \Rep(S);\, q \getsr \calQ :
\mathrm{Err}(S,q,M,\pubaux,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
\end{definition}

@@

\todo{Add discussion of just how broad the syntax is, in general.}

>>>>

\heading{Data structures.}  We being by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset.
%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$, and a set of multisets~$\calS$ over
$\univ$. 
A \emph{data structure} (for $\calS$) is a tuple $\setprim=(\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
\item $\Rep \colon \mathcal{S} \to \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
    \emph{public representation data} $\pubaux \in \bits^*$ and
    \emph{private representation data} $\privaux \in \bits^*$. We write
    $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
\item $\Qry\colon \Sigma^* \times \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $\pubaux,\privaux \in
    \bits^*$ and $q \in \calQ$, and outputting
    an \emph{answer} $a \in \Gamma$.  We write $a \gets
    \Qry(\pubaux,\privaux,q)$ for this execution.
\end{itemize}
\hfill\dqed
\end{definition}

@@

\begin{definition}[Error probability and rate] \rm
Fix a data structure $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep,
\Qry)$. Let $\mathrm{Err}(S,q,\pubaux,\privaux)$ be a predicate that is
true iff $\Qry(\pubaux,\privaux, q) \neq q(S)$.  Then a data structure
has \emph{error probability} $\epsilon$ if
$\max_{S,q}\Pr[(\pubaux,\privaux) \getsr \Rep(S) :
\mathrm{Err}(S,q,\pubaux,\privaux)=1 ] \leq \epsilon$.
%
It has \emph{error rate} $\tilde{\epsilon}$ if
$\max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, q \getsr \calQ :
\mathrm{Err}(S,q,\pubaux,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
\end{definition}

@@
